\documentclass{l4proj}

%
% put any packages here
%

\begin{document}
\title{HCI4 Coursework}
\author{Michael McFadyen}
\date{November 2013}
\maketitle

%
%NOTE: if you include the educationalconsent (above) and your project is graded an A then
%      it may be entered in the CS Hall of Fame
%
\tableofcontents
%==============================================================================

\chapter{Introduction}
\pagenumbering{arabic}
The first page, abstract and table of contents are numbered using Roman numerals. From now on pages are numbered
using Arabic numerals. Therefore, immediately after the first call to $\backslash$chapter we need the call
$\backslash$pagenumbering$\{$arabic$\}$ and this should be called once only in the document. 

The first Chapter should then be on page 1. You are allowed 50 pages for a 30 credit project and 35 pages for a 
20 credit report. This includes everything up to but excluding the appendices and bibliograph, i.e. this is a limit on
the body of the report.

You are not allowed to alter text size (it is currently 11pt) neither are you allowed to alter the margins.

Note that in this example, and some of the others, you need to execute the following commands the first time you process the files.
Multiple calls to pdflatex are required to resolve references to labels and citations. The file bib.bib is the bibliography file.


\chapter{Design}

\section{Prototypes}

\section{Prototype Evaluation}

\section{Redesigned Prototypes}


\chapter{Implementation}

\chapter{Evaluation}


\chapter{Conclusion}
\begin{verbatim}

            > pdflatex example0
            > bibtex example0
            > pdflatex example0
            > pdflatex example0

\end{verbatim}

%%%%%%%%%%%%%%%%
%              %
%  APPENDICES  %
%              %
%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%   BIBLIOGRAPHY   %
%%%%%%%%%%%%%%%%%%%%

\end{document}
